Template for indicator documentation

### 2023-10-20 NDVI_wetland.Rmd
updating tables and minor edits

<!-- Load all you dependencies here -->
```{r setup, include=FALSE}
library(downloader)
library(data.table)
library(lubridate)
library(sf)
library(plyr)
library(stringr)
library(tidyverse)
library(RColorBrewer)
library(gridExtra)
library(ggridges)
library(tmap)
library(tmaptools)
library(betareg)
library(StepBeta)
library(glmmTMB)
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r, echo=FALSE}
metaData <- data.frame(Ecosystem,
  "Økologisk egenskap" = Egenskap,
  "ECT class" = ECT
)
knitr::kable(metaData)
```

>>>>

<!-- Load all you dependencies here -->
```{r setup, include=FALSE}
library(downloader)
library(data.table)
library(lubridate)
library(sf)
library(plyr)
library(stringr)
library(tidyverse)
library(RColorBrewer)
library(gridExtra)
library(ggridges)
library(tmap)
library(tmaptools)
library(betareg)
library(StepBeta)
library(glmmTMB)
library(knitr)
library(flextable)
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r, echo=FALSE}
metaData <- data.frame(Ecosystem,
                       "Økologisk egenskap" = Egenskap,
                       "ECT class" = ECT,
                       check.names = F)
flextable(metaData) %>%
  bg(bg = "lightblue", part="header") %>%
  theme_vanilla() %>%
  set_table_properties(layout = "autofit")
```

### 2023-10-20 functional_plant_indicators_natopen.Rmd
updating tables and minor edits

# Functional Plant Indicators - Naturally Open Ecosystems {#Functional-plant-indicators-open}

@@

<!-- Load all you dependencies here -->
```{r setup, include=FALSE}
library(readxl)
library(sf)
library(plyr)
library(tidyverse)
library(RColorBrewer)
library("gridExtra") 
library(ggridges)
library(tmap)
library(tmaptools)
library(raster)
library(stars)
library(betareg)
library(glmmTMB)
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r, echo=FALSE}
metaData <- data.frame(Ecosystem,
                       "Økologisk egenskap" = Egenskap,
                       "ECT class" = ECT)
knitr::kable(metaData)
```

>>>>

# Functional Plant Indicators - Naturally Open Ecosystems {#functional-plant-indicators-open}

@@

<!-- Load all you dependencies here -->
```{r setup, include=FALSE}
library(readxl)
library(sf)
library(plyr)
library(tidyverse)
library(RColorBrewer)
library("gridExtra") 
library(ggridges)
library(tmap)
library(tmaptools)
library(raster)
library(stars)
library(betareg)
library(glmmTMB)
library(knitr)
library(flextable)
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r, echo=FALSE}
metaData <- data.frame(Ecosystem,
                       "Økologisk egenskap" = Egenskap,
                       "ECT class" = ECT,
                       check.names = F)
flextable(metaData) %>%
  bg(bg = "lightblue", part="header") %>%
  theme_vanilla() %>%
  set_table_properties(layout = "autofit")
```

### 2023-10-20 functional_plant_indicators_seminat.Rmd
updating tables and minor edits

# Functional Plant Indicators - Semi-Natural Ecosystems {#Functional-plant-indicators-seminat}

@@

<!-- Load all you dependencies here -->
```{r setup, include=FALSE}
library(readxl)
library(sf)
library(plyr)
library(tidyverse)
library(RColorBrewer)
library("gridExtra") 
library(ggridges)
library(tmap)
library(tmaptools)
library(raster)
library(stars)
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```

>>>>

# Functional Plant Indicators - Semi-Natural Ecosystems {#functional-plant-indicators-seminat}

@@

<!-- Load all you dependencies here -->
```{r setup, include=FALSE}
library(readxl)
library(sf)
library(plyr)
library(tidyverse)
library(RColorBrewer)
library("gridExtra") 
library(ggridges)
library(tmap)
library(tmaptools)
library(raster)
library(stars)
library(knitr)
library(flextable)
knitr::opts_chunk$set(echo = TRUE)
```

### 2023-10-20 insectIndicators.Rmd
updating tables and minor edits

<!-- This is a template for how to document the indicator analyses.

Make a copy of this file and store it in the root folder (same as where this template is stored) folder. 
Name te file DRAFT_myIndicatorName.Rmd.

Because this is a stand-alone Rmd file inside a bookdown project, in order to knit the file for preview purposes,
you need to type rmarkdown::render("template.Rmd") in the console, 
as the the usual Ctrl + Alt + k will not work.

Make sure also to not change the order, or modify the headers, unless you really need to. This is because it
easier to read the web page as a whole of the indicators are presented using the same layout.

When the analyses is complete, Anders Kolstad, or someone else, will perform a rapid code review, making sure 
the analysis is repeatable by someone else. Be therefore very careful to annotate 
and comment on every step in the analysis. When completed, Anders will make a copy
of the working file and put it in the same project root folder, but removing the 'DRAFT_' part of the name. 
After modifying it slightly (mainly removing the top YAML header and updating the rmd_files argument in '_bookdown.yml') 
the output will become available on the website (https://ninanor.github.io/ecosystemCondition/). -->

<!-- Examples:

For an example, see 'indicators/breareal-workingFile.Rmd' 
and the subsequent 'breareal.Rmd' 
which again, when rendered, produces this:
https://ninanor.github.io/ecosystemCondition/areal-av-isbreer.html

Notice the degree of annotation.

-->

<!-- Replace 'indicator name' with yor own indicator name  -->
# Insect indicators

@@

_Author and date:_
Jens Åström `r Sys.Date()`

@@

suppressPackageStartupMessages({
require(Norimon)
require(bombLepiSurv)
require(tmap)
require(sf)
require(tidyverse)
})

@@

<!-- Fill in which ecosystem the indicator belongs to, as well as the ecosystem characteristic it should be linked to. It's OK to use some Norwegian here -->
```{r, echo=F}
Ecosystem <- rep("Semi-naturlig mark", 3) # e.g. "Skog og fjell"
Egenskap  <- c("Biologisk mangfold, Funksjonelle grupper innen trofiske nivåer, Funksjonelt viktige arter og biofysiske strukturer") # e.g. "Primærproduksjon"
ECT       <- rep("Functional state characteristics", 3) # e.g. "Structural state characteristic"
Contact   <- rep("Jens Åström", 3) # e.g. "Anders Kolstad"
```

```{r, echo=F}
metaData <- tibble(Ecosystem,
                       "Økologisk egenskap" = Egenskap,
                       "ECT class" = ECT)
knitr::kable(metaData)
```

>>>>

# Insect indicators

@@

_Author and date:_

Jens Åström `r Sys.Date()`

@@

suppressPackageStartupMessages({
require(Norimon)
require(bombLepiSurv)
require(tmap)
require(sf)
require(tidyverse)
require(flextable)
})

@@

<!-- Fill in which ecosystem the indicator belongs to, as well as the ecosystem characteristic it should be linked to. It's OK to use some Norwegian here -->
```{r, echo=F}
Ecosystem <- rep("Semi-naturlig mark", 3) 
Egenskap  <- c("Biologisk mangfold", 
               "Funksjonelle grupper innen trofiske nivåer", 
                "Funksjonelt viktige arter og biofysiske strukturer") 
ECT       <- rep("Functional state characteristics", 3) 
Contact   <- rep("Jens Åström", 3)
```

```{r, echo=F}
metaData <- data.frame(Ecosystem,
                       "Økologisk egenskap" = Egenskap,
                       "ECT class" = ECT,
                       check.names = F)
flextable(metaData) %>%
  bg(bg = "lightblue", part="header") %>%
  theme_vanilla() %>%
  set_table_properties(layout = "autofit")
```
